\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{School of random department names} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge This is the title of the template report \\ \horrule{2pt} \\[0.5cm]

### 2018-05-17 Report/notes.tex
last modif

\lstset{frame=tb,
	aboveskip=3mm,
	belowskip=3mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\small\ttfamily\color{red}},
	numbers=none,
	numberstyle=\tiny\color{blue},
	keywordstyle=\color{black},
	commentstyle=\color{dkgreen},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3,
	morekeywords={\;,init,gsmp,dtmc, const, int, double, module, formula, endmodule,->,=} 
}
%%% Begin document
\begin{document}
	\maketitle
	\begin{abstract}
		The subject of this internship is first modeling some system  in the PrismGSMP. That is a continuous system with rates instead of probabilistic transition. Transitiom are syncronized with event which follows some probabilistic laws like exponential law or dirac. One good property about the exponenial law is the events are markovian. That is the probability of the event of happening doenst depends on the time already spend.

@@

		const int qCapacity = 10;

		module main
		event prod = dirac(timeout);

		[produce] (qSize < qCapacity)--prod -> (qSize' = qSize+1);
		[consume] (qSize > 0) -> lambda: (qSize' = qSize - 1);

		endmodule
		\end{lstlisting}
		\caption{Prism code for figure \ref{fig:Queue1}}
		\label{fig:queuecode1}
	\end{figure}

@@

>>>>

\definecolor{prismgreen}{rgb}{0, 0.6, 0}

%% BEGIN PRISM CODE LISTING 
\lstdefinelanguage{Prism}{ % syntax highlight via font
	basicstyle=\color{red}\tiny\ttfamily, % small true type font (like
	courier)
	morekeywords={bool,C,ceil,const,ctmc,double,dtmc,endinit,endmodule,endrewards,endsystem,F,false,floor,formula,G,global,I,init,int,label,max,mdp,min,module,nondeterministic,P,Pmin,Pmax,prob,probabilistic,R,rate,rewards,Rmin,Rmax,S,stochastic,system,true,U,X},
	keywordstyle={\bfseries\color{black}},
	numberstyle=\tiny\color{black},
	comment=[l] {//}, morecomment=[s]{/*}{*/}, % single and multi-line
	commentstyle= \color{prismgreen}, % dark green
	tabsize=4, % tab treatment (going to be fixed in Prism)
	captionpos=b, % put captions at the bottom
	escapechar=@ % write LaTeX comments escaped by @ symbol
}

%define command \prism with one argument for inline printing of \prismcode
\newcommand{\prism}[1]{\lstinline[language=Prism,basicstyle=\small
	\ttfamily]|#1|}

%% END PRISM CODE LISTING

     % Set your language (you can change the language for each code-block optionally)

%%% Begin document
\begin{document}
	\maketitle
	\begin{abstract}
		The subject of this internship is first modeling some system  in the PrismGSMP. That is a continuous system with rates instead of probabilistic transition. Transitiom are syncronized with event which follows some probabilistic laws like exponential law or dirac. One good property about the exponenial law is the events are markovian. That is the probability of the event of happening doenst depends on the time already spend.

@@

	\begin{figure}
		\centering
		\lstinputlisting[language=Prism]{../Model/timeoutqueue.sm}

		\caption{Prism code for figure \ref{fig:Queue1}}
		\label{fig:queuecode1}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{size.png}
		\caption{size of model versus k}
		\label{fig:time1}
	\end{figure}
